Is Crime Really On A Rise In Toronto? An Analysis of The Past And Current Crime Rates of Toronto

### 2024-01-24 outputs/paper/paper.qmd
Changed number of decimals to 2 and updated README

head(cleaned_crime_rates_data) |> kable(col.names = c("Crime", "Year", "Crime Rate"))
```

@@

head(average_crime_rates_per_year) |> kable(col.names = c("Crime", "Year", "Average Crime Rate"))
```

@@

final_percentage_change_table |> select("Crime", "Percentage Change") |> kable()
```

@@

colnames(percentage_change_table) <- c("X", "Crime", "Percentage Change")
percentage_change_table |> select("Crime", "Percentage Change") |> kable()
```

>>>>

head(cleaned_crime_rates_data) |> kable(col.names = c("Crime", "Year", "Crime Rate"), digits = 2)
```

@@

head(average_crime_rates_per_year) |> kable(col.names = c("Crime", "Year", "Average Crime Rate"), digits = 2)
```

@@

final_percentage_change_table |> select("Crime", "Percentage Change") |> kable(digits = 2)
```

@@

colnames(percentage_change_table) <- c("X", "Crime", "Percentage Change")
percentage_change_table |> select("Crime", "Percentage Change") |> kable(digits = 2)
```
